Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-07-21 src/ms.tex
Updated paper

\begin{abstract}
	Globular Clusters (GCs) provide a unique astrophysical laboratory for
	studying the formation and evolution of stars. GCs are old, dense, and it
	has historically been believed that they have a single stellar population
	(SSP, in some publications also simple stellar population). However, in the
	last two decades, it has been definitively shown that most if not all Milky
	Way GCs have multiple stellar populations (MPs). These MPs are chemically
	distinct from one another, primarily separated by light element abundance
	variations without the standard accompanying heavy element abundance
	variations. In addition to the light element abundance variations, MPs also
	have different inferred helium abundances. The origin of these MPs remains
	an open question, and one which is sensitive to the population - population
	compositional differences; consequently, the extent of the composition
	variations is a key parameter to constrain. Metal abundances may be
	directly measured spectroscopically; however, helium abundances are not
	directly observable in GCs. Instead, helium abundances are inferred from
	stellar models. It is therefore important to understand build stellar
	models that are self-consistent in the compositions of the structure,
	atmosphere, and opacity. In this work we present the first chemically
	self-consistent stellar models of the Milky Way Globular Cluster NGC 2808.
	We find that the helium abundance of the second generation of stars is
	higher than the first generation by {\color{red} SOME AMOUNT}.
	{\color{blue} This is in agreement with previous studies of NGC 2808.}
\end{abstract}

>>>>

\begin{abstract}
	Globular Clusters (GCs) provide a unique astrophysical laboratory for
	studying the formation and evolution of stars. GCs are old, dense, and it
	has historically been believed that they have a single stellar population. However, in the
	last two decades, it has been definitively shown that most if not all Milky
	Way GCs have multiple stellar populations (MPs). These MPs are chemically
	distinct from one another, primarily separated by light element, including helium, abundance
	variations without the standard accompanying heavy element abundance
	variations. As the precise formation channel of these MPs remains
	an open question, and one which is sensitive to the population - population
	compositional differences, the extent of the composition
	variations between MPs is a key parameter to constrain. Many metal abundances may be
	directly measured spectroscopically; however, helium abundances are not
	directly observable in GCs. Instead, helium abundances are inferred from
	stellar models. It is therefore important to understand build stellar
	models that are self-consistent in the compositions of the structure,
	atmosphere, and opacity. In this work we present the first chemically
	self-consistent stellar models of the Milky Way Globular Cluster NGC 2808 using MARCS model atmospheres, OPLIB high-temperature radiative opacities, and AESOPUS low-temperature radiative opacities.
	We find that the helium abundance of the second generation of stars is
	higher than the first generation by {\color{red} SOME AMOUNT}.
	{\color{blue} This is in agreement with previous studies of NGC 2808.}
\end{abstract}

### 2023-07-21 src/sections/AtmopshericModels.tex
Updated paper

\section{Chemical Consistency}\label{sec:const}
There are three primary areas in which must the stellar models must be
consistent: the atmospheric boundary conditions, the opacities, and interior
abundances. The interior abundances are relatively easily handled by adjusting
parameters within our stellar evolutionary code. However, the other two areas are
more complicated to bring into consistency. Atmospheric boundary conditions and
opacities must both be calculated with a consistent set of chemical abundances
outside of DSEP. The

\subsection{Atmospheric Boundary Conditions}\label{sec:atm}
Certain assumptions {\color{red}[WHICH ONES,CITATION]} made in stellar structure
codes, such as DSEP, are valid when the optical depth of a star is small.
However, in the atmospheres of stars, the number density of particles drops low
enough and the optical depth consequently becomes large enough that these
assumptions break down, and more separate plasma modeling code is required.
Generally structure code will use tabulated atmospheric boundary conditions
generated by these specialized codes {\color{red} PHEONIX, ATLAS, MARCS +
[CITATIONS]}. Often, as the boundary conditions are both expensive to compute
and not the speciality of stellar structure researchers, the boundary
conditions are not updated as as light-element interior abundance varies.

>>>>

\section{Chemical Consistency}\label{sec:const}
There are three primary areas in which must the stellar models must be made chemically
consistent: the atmospheric boundary conditions, the opacities, and interior
abundances. The interior abundances are relatively easily handled by adjusting
parameters within our stellar evolutionary code. However, the other two areas are
more complicated to bring into consistency. Atmospheric boundary conditions and
opacities must both be calculated with a consistent set of chemical abundances
outside of the stellar evolution code. For evolution we use the Dartmouth Stellar Evolution Program (DSEP) \citep{Dotter2008}, a well tested 1D stellar evolution code which has a particular focus on modelling low mass stars ($\le 2$ M$_{\odot}$)

\subsection{Atmospheric Boundary Conditions}\label{sec:atm}
Certain assumptions, primarily that the radiation field is at equilibirum and radiative transport is diffusive \citep{Salaris2005}, made in stellar structure
codes, such as DSEP, are valid when the optical depth of a star is small.
However, in the atmospheres of stars, the number density of particles drops low
enough and the optical depth consequently becomes large enough that these
assumptions break down, and separate, more physically motivated, plasma modeling code is required.
Generally structure code will use tabulated atmospheric boundary conditions
generated by these specialized codes ATLAS9 \citep{Kurucz1993}, PHEONIX \citep{Husser2013}, MARCS \citep{Gustafsson2008}, and MPS-ATLAS \citep{Kostogryz2023}. Often, as the boundary conditions are both expensive to compute
and not the speciality of stellar structure researchers, the boundary
conditions are not updated as as light-element interior abundance varies.
